Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-07-16 drafts/outline.tex
sorted out figure references

\begin{figure}[htbp]
\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
\centering
\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:capeff}
\end{figure}

@@

Our experiment was conducted in a recirculating flume. Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity) with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure TODO). In the upper range of the pump's span, cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise. By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump stayed free of cavitation up to a rotation frequency well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.

\begin{figure}[htbp]
TODO
\centering
\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:floorplan}
\end{figure}

>>>>

\begin{figure}[htbp]
\includegraphics[width=10cm]{pics/collectorefficiency.png}
\centering
\caption{Particle capture efficiency diagram (TODO: caption)} \label{fig:capeff}
\end{figure}

@@

Our experiment was conducted in a recirculating flume. Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity) with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}). In the upper range of the pump's span, cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise. By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump stayed free of cavitation up to a rotation frequency well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.

\begin{figure}[htbp]
TODO
\centering
\caption{flume floorplan}
\label{fig:floorplan}
\end{figure}
